---
title: "Coffee Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 5)

# packages
library(tidymodels)
library(tidyverse)
```

I am going to try and fit a model that predicts coffee reviews using a coffee data set I found. This is a data set from the Coffee Quality Institute's webpage, it consists of quality reviews of different brands of coffee. My goal is to try and come up with a model that will predict a coffee's quality score. 

```{r}
coffee <- read_csv(here::here("Coffee/arabica_ratings_raw.csv"))
```

## Data Cleaning

I first need to do a little bit of data cleaning. I want to select the columns that relate to the coffee quality score and remove any meta data columns that came with the data. I will also need to make sure that each of the columns that show the different parts of the review use the same units of measurement.

```{r}
# overview of data set
glimpse(coffee)
```


## Explore data


## Build models


## Evaluate models
