---
title: "Coffee Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 5)

# packages
library(tidymodels)
library(tidyverse)
```

I am going to try and fit a model that predicts coffee reviews using a coffee data set I found. This is a data set from the Coffee Quality Institute's webpage, it consists of quality reviews of different brands of coffee. My goal is to try and come up with a model that will predict a coffee's quality score. 

```{r}
coffee <- read_csv(here::here("Coffee/arabica_ratings_raw.csv"))
```

## Data Cleaning

I first need to do a little bit of data cleaning. I want to select the columns that relate to the coffee quality score and remove any meta data columns that came with the data. I will also need to make sure that each of the columns that show the different parts of the review use the same units of measurement.

```{r}
# overview of data set
glimpse(coffee)
```

```{r}
# remove meta data columns
coffee_clean <- coffee %>%
  select(-contains("NA")) %>%
  select("ID" = `...1`, quality_score,
         Aroma, Flavor, Aftertaste, Acidity,
         Body, Balance, Uniformity, `Clean Cup`, 
         Sweetness, Moisture, `Category One Defects`, Quakers,
         Color, `Category Two Defects`) %>%
  distinct()

# quick look to make sure columns are all the right type
glimpse(coffee_clean)

# convert moisture clean to numeric
coffee_clean <- coffee_clean %>%
  mutate(Moisture = str_extract(Moisture, "[0-9]+"),
         Moisture = as.numeric(Moisture),
         Moisture = Moisture/100)

# make defect columns numeric
coffee_clean <- coffee_clean %>%
  mutate_at(vars(contains("Defects")), list(~str_extract(., "[0-9]+"))) %>%
  mutate_at(vars(contains("Defects")), list(~as.numeric(.)))

# fix column names
coffee_clean <- coffee_clean %>%
  janitor::clean_names()

# check for NAs
nas <- coffee_clean %>%
  filter_all(any_vars(is.na(.)))

# most color NA, will replace with a 'not listed'
# one na in quakers, will remove
coffee_clean <- coffee_clean %>%
  mutate(color = if_else(is.na(color), "Not Listed", color)) %>%
  filter(!is.na(quakers))
```

## Explore data

```{r}
# historgram
coffee_clean %>%
  ggplot(aes(quality_score)) + 
  geom_histogram(fill = "darkgreen", alpha = 0.8)

# some interesting outliers, better do a boxplot to confirm
coffee_clean %>%
  ggplot(aes(quality_score)) + 
  geom_boxplot()

# pretty normally distributed data, but there are a few outliers towards the lower end of the data
summary(coffee_clean$quality_score)

# look at those with 0 quality score
# one observation where most columns are just '0'
check_quality <- coffee_clean %>%
  filter(quality_score == 0)

# remove one zero outliers 
# historgram
coffee_clean %>%
  filter(quality_score != 0) %>%
  ggplot(aes(quality_score)) + 
  geom_histogram(fill = "darkgreen", alpha = 0.8)

coffee_clean <- coffee_clean %>%
  filter(quality_score != 0)

# some common scatter plots
# pretty decent linear relationship 
coffee_clean %>%
  ggplot(aes(quality_score, aroma)) + 
  geom_point() 

coffee_clean %>%
  ggplot(aes(quality_score, acidity)) + 
  geom_point()

coffee_clean %>%
  ggplot(aes(quality_score, body)) + 
  geom_point()

# a breakdown of quality score by binned aftertaste
coffee_clean %>%
  filter(!is.na(aftertaste)) %>%
  mutate(aftertaste = cut_number(aftertaste, 4)) %>%
  ggplot(aes(aftertaste, quality_score, fill = aftertaste)) +
  geom_boxplot(alpha = 0.2, show.legend = FALSE)
```


## Build model

```{r}
set.seed(123)
coffee_clean <- initial_split(data = coffee_clean, strata = quality_score)
coffee_train <- training(coffee_clean)
coffee_test <- testing(coffee_clean)

set.seed(234)
coffee_folds <- vfold_cv(coffee_train, strata = quality_score)


xgb_spec <-
  boost_tree(
    trees = tune(),
    mtry = tune(),
    min_n = tune(),
    learn_rate = tune(),
    loss_reduction = tune(),
    sample_size = tune()
  ) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

coffee_rec <- 
  recipe(quality_score ~ ., data = coffee_train) %>%
  update_role(id, new_role = "ID") %>%
  step_string2factor(all_nominal_predictors()) %>%
  step_normalize(all_numeric_predictors()) %>%
  step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors()) 


xgb_wf <- workflow(coffee_rec, xgb_spec)

# tune the model
doParallel::registerDoParallel()

set.seed(234)
xgb_coffee_rs <-
  tune_grid(
    xgb_wf,
    coffee_folds,
    grid = 20
  )
```



## Evaluate model

```{r}
show_best(xgb_coffee_rs, metric = "rsq")

xgb_last <-
  xgb_wf %>%
  finalize_workflow(select_best(xgb_coffee_rs, "rsq")) %>%
  last_fit(coffee_clean)

library(vip)
xgb_fit <- extract_fit_parsnip(xgb_last)
vip(xgb_fit, geom = "point", num_features = 12)
```

It seems that the most important variables in the quality score are flavor, clean_cup and aftertaste. 